Add Plant Functional Type (PFT) labels

### 2021-04-05 R/add_plant_functional_type.Rmd
working on merging growthForm data to spectra by uid

>>>>

## Use NEON growthForm observations

```{r}
library(neonUtilities)
```

```{r}
# download woody vegetation structure data for all sites and years 
out_dir <- here::here("analysis","data","raw_data")

neonUtilities::zipsByProduct(dpID = "DP1.10098.001",
              savepath = out_dir,
              check.size = FALSE)

stackByTable(file.path(out_dir, "filesToStack10098"), folder = TRUE)
```

```{r}
# read the vst_apparentindividual table, which has growthForm data

vst_apparentindividual <- read_csv(out_dir <- here::here("analysis","data","raw_data", "filesToStack10098",
                                                         "stackedFiles", "vst_apparentindividual.csv"))

growthForms <- vst_apparentindividual %>% 
  select(uid, growthForm)

# merge the growthForm column into the spectra data by uid 
cleaned_spectra_merged <- merge(cleaned_spectra, growthForms, by = "uid", all.x=TRUE)

```{r}
# summarize the downloaded growthform data to see which growth forms are assigned to each species 
growthForms %>% 
    distinct(uid, .keep_all = TRUE) %>% 
    group_by(growthForm) %>% 
    tally()

# summarize the merged growthform data
